No Dogs On The Couch$_{Base}$

### 2012-11-20 Assignment6/paper/paper.tex
Basic introduction done. Removed one of the nested evaluation sections of analysis about conclusions of comparisons of data about the results of our experiments on the evaluation on couchbase and mysql.

\section{Introduction}
TODO

@@

\section{Analysis}
TODO

>>>>

\section{Introduction}
Our team decided to compare a MySQL cluster versus a Couchbase cluster for running a
web application. We are using an eight table SQL schema from Ryan Verdon's Thesis. To evaluate
the performance we autogenerated around 400MB of data and inserted the same data into each cluster.
Obviously using a different data model for Couchbase to accomodate for the fact it is a NoSQL key-value store
instead of a relational database. We then created a set of six experiments to run. Five came from common 
use cases found in the web application. While the other was designed to test the performance on each cluster
of repeatedly writing and reading from the same object. Our major metrics are write performance, read performance,
and time-delay between writes and reads of the same data. The rest of the paper is broken down as follows.
Section 2 describes in depth how we designed the experiment. Section 3 discusses our implementation. Section 4 goes
into the results of each of our experiments and some analysis on the data we obtained. Lastly, section 5 presents 
our conclusions.

@@
